---
title: "US COVID Dashboard"
output: 
  flexdashboard::flex_dashboard:
    logo: corona.png
    source_code: "https://github.com/m-jmc/US-COVID-Tracing"

---

<style>                     
.navbar {
  background-color:black;
  border-color:black;
}
.navbar-brand {
color:white!important;
}
</style> 


```{r setup, include=FALSE}


# Logo file 48 pixels High
 
library(flexdashboard) 
library(highcharter)
library(plotly) 
library(viridis)
library(tidyverse)
library(crosstalk)
library(RColorBrewer)
library(scales)
library(ggrepel)
library(lubridate)
library(formattable)
library(maps)
library(usmap)
library(leaflet)
library(rgdal)
library(deSolve)
library(gridExtra)
library(formattable)
library(tigris)
library(reshape2)


# Create brewer blues palette with greater than 9 colors:
# Classic palette BuPu, with 4 colors
Xtra_Blue <- brewer.pal(9, "Blues") 
# Add more colors to this palette :
Xtra_Blue <- colorRampPalette(Xtra_Blue)(15)

ltblue = "#86baf9"
drkblue = "#095dc3"
# Plot it
#pie(rep(1, length(Xtra_Blue)), col = Xtra_Blue , main="") 

```


```{r, echo=FALSE, include=FALSE}

# Use two days ago as the "latest date" to accommodate reporting delays or dataset updates
latest_date <- list(Sys.Date()-2)

# Import dataset
#data <- read_csv("us-counties.csv")
raw <- "https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv"
data <- read_csv(raw)


# Creating df of state and county populations from 2015 census estimates part of the usmap package
us.county.pop <- countypop
us.state.pop <- statepop %>% rename(state = full)


#Joining county population estimates to the case/death estimates 
us.recent <- data %>% 
             filter(date==latest_date) %>% 
             subset(select=c("fips","cases","deaths","state")) %>% 
             left_join(us.county.pop, by=c("fips"))

# create per capital (10,000) calculations
us.recent$Confirmed_Per_Capita <- round(us.recent$cases/us.recent$pop_2015*10000,2)
us.recent$Deaths_Per_Capita <- round(us.recent$deaths/us.recent$pop_2015*10000,2)

# Create a GEOID column to merge with the sp object for leaflet mapping
us.recent$GEOID <- us.recent$fips

# Create the US county sp object from the tigris package and merge the calculated rates to the map
us.sp <- counties(cb = TRUE)
us.sp <- sp::merge(us.sp,us.recent, by="GEOID")

#Set the color palette (viridis package option a = Magma)
#uspal <- colorNumeric("magma", domain=us.sp$Confirmed_Per_Capita, na.color="transparent")
uspal <- colorQuantile(Xtra_Blue, domain=us.sp$Confirmed_Per_Capita, n=10, na.color="transparent")
# Set the popup text option
uspopup_t <- paste0("State: ", as.character(us.sp$state),  "<br>",
  "County: ", as.character(us.sp$NAME),  "<br>", 
                  "Confirmed Cases Per 10,000 Residents: ", as.character(us.sp$Confirmed_Per_Capita),  "<br>",
                  "Total Cases: ", as.character(us.sp$cases))


```


National {data-orientation=columns data-icon="ion-android-globe"}
=======================================================================

```{r, echo=FALSE, include=FALSE}

# Reformatting the latest date as a data frame, renaming the column to last week to subtract 7 days, also create month df here as well
latest_date.df <- as.data.frame(latest_date) 
names(latest_date.df)[1]<-paste("Date")
LastWeek.df <- latest_date.df$Date - 7
LastMonth.df <- latest_date.df$Date - 30
LatestDate.df <- latest_date.df$Date

# group and summarize for state level counts
state <- data %>%
         subset(select = c("state","date","cases","deaths")) %>%
         group_by(state, date) %>%
         summarise(cases = sum(cases), deaths = sum(deaths))

state <- state %>% 
         left_join(us.state.pop[,c("state","pop_2015")], by=c("state")) %>% 
         rename(Population = pop_2015)

# Per Capita rates are per 100,000 using 2015 state population estimates
state$`Cases per Capita` <- round(state$cases/state$Population*100000,2)
state$`Deaths per Capita` <- round(state$deaths/state$Population*100000,2)

# Take current counts and counts from last week and last month
state.week <- state %>% filter(date == (LastWeek.df)) %>% rename(lastweek = cases)
state.month <- state %>% filter(date == (LastMonth.df)) %>% rename(lastmonth = cases)
state.current <- state %>% filter(date == (LatestDate.df)) %>% rename(currentcases = cases)

# Join counts from last week and last month to a single dataframe
state.current <- state.current %>% left_join(state.week[,c("state","lastweek")], by=c("state"))
state.current <- state.current %>% left_join(state.month[,c("state","lastmonth")], by=c("state"))

# calculate rates per capita growth over past week and month
state.current$lastweek_percapita <- round(state.current$lastweek/state.current$Population*100000,2)
state.current$lastmonth_percapita <- round(state.current$lastmonth/state.current$Population*100000,2)

# % difference between current and previous (week / month) per capita values
state.current$`Past Week Change CPC` <- percent(round((state.current$`Cases per Capita` - state.current$lastweek_percapita) / 
                                 ((state.current$`Cases per Capita` + state.current$lastweek_percapita)/
                                    2),2))

state.current$`Past Month Change CPC` <- percent(round((state.current$`Cases per Capita` - state.current$lastmonth_percapita) /
                                       ((state.current$`Cases per Capita` + state.current$lastmonth_percapita)/
                                          2),2))

state.tbl <- state.current %>% subset(select = c("state",
                                                 "Population",
                                                 "currentcases",
                                                 "Cases per Capita",
                                                 "Deaths per Capita",
                                                 "Past Week Change CPC",
                                                 "Past Month Change CPC")) %>% 
                                      rename(State=state,
                                             `Current Cases`=currentcases) %>%
                                      arrange(desc(`Past Week Change CPC`)) 


state.formattable <- state.tbl %>%
                formattable(align =c("l","l","l","c","c","c","c"),
                list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
                `Past Week Change CPC` = color_bar(ltblue)))


```


Column {data-width=200}
-------------------------------------

### New Cases <font size='1'> Yesterday </font>

```{r fig.height=0.8}

# Not straightforard, but taking the case count from 2 and 3 days ago and summarising by date to create a df of two values
new.cases <- state %>%
              filter(date == (Sys.Date()-2) | date == (Sys.Date()-3)) %>%
              subset(select = c("date","cases")) %>%
              group_by(date) %>%
              summarise(cases = sum(cases)) %>%
              subset(select = c("cases")) %>%
              melt(id.var="cases")

# There has got to be a better way to do this, but subtracting the second row (which is the most recent date) from the first to get the total new cases               
new.cases <- new.cases[2, ] - new.cases[1, ]
new.cases <- format(new.cases$cases,big.mark=",",scientific=FALSE)

# # Using table indexs to subtract resulting rows
# new.cases <- rbind(new.cases, new.cases[2, ] - new.cases[1, ])

# Create value box
valueBox(new.cases, icon = "ion-ios-medkit", color = "rgb(9, 93, 195)")


```

### Deaths <font size='1'> Yesterday </font>

```{r fig.height=0.8}

new.deaths <- state %>%
              filter(date == (Sys.Date()-2) | date == (Sys.Date()-3)) %>%
              subset(select = c("date","deaths")) %>%
              group_by(date) %>%
              summarise(deaths = sum(deaths)) %>%
              subset(select = c("deaths")) %>%
              melt(id.var="deaths")

# There has got to be a better way to do this, but subtracting the second row (which is the most recent date) from the first to get the total new cases               
new.deaths <- new.deaths[2, ] - new.deaths[1, ] 
new.deaths <- format(new.deaths$deaths,big.mark=",",scientific=FALSE)


valueBox(new.deaths, icon = "ion-ios-close", color = "rgb(9, 93, 195)")

```

### Total US Cases <font size='1'> All Time </font>

```{r fig.height=0.8}

total.cases <- data %>%
              filter(date == (Sys.Date()-2)) %>%
              subset(select = c("cases")) %>%
              summarise(cases = sum(cases)) 

total.cases <- format(total.cases$cases,big.mark=",",scientific=FALSE)


valueBox(total.cases, icon = "ion-ios-medkit-outline", color = "rgb(134, 186, 249)")

```


### Total US Deaths <font size='1'> All Time </font>

```{r fig.height=0.8}

total.deaths <- data %>%
              filter(date == (Sys.Date()-2)) %>%
              subset(select = c("deaths")) %>%
              summarise(deaths = sum(deaths)) 

total.deaths <- format(total.deaths$deaths,big.mark=",",scientific=FALSE)


valueBox(total.deaths, icon = "ion-ios-close-outline", color = "rgb(134, 186, 249)")

```

### {.no-padding}

```{r fig.height=0.8}

# Mapping state abrv to region for regional case summary
# Source: https://stackoverflow.com/questions/46066974/add-column-to-label-u-s-states-by-their-u-s-census-region

NE.abrv <- c("CT","ME","MA","NH","RI","VT","NJ","NY","PA")
MW.abrv <- c("IN","IL","MI","OH","WI","IA","KS","MN","MO","NE","ND","SD")
S.abrv <- c("DE","DC","FL","GA","MD","NC","SC","VA","WV","AL","KY","MS","TN","AR","LA","OK","TX")
W.abrv <- c("AZ","CO","ID","NM","MT","UT","NV","WY","AK","CA","HI","OR","WA")

region.list <- list(
               Northeast=NE.abrv,
               Midwest=MW.abrv,
               South=S.abrv,
               West=W.abrv)

# This creates a list column of the regions, which needs to be unnested before grouping 
us.recent$Region <- sapply(us.recent$abbr, function(x) names(region.list)[grep(x,region.list)])
us.recent <- us.recent %>%
             unnest(cols = c(Region))

# without a unique ID to match on, I created an id column with the row number to prevent duplicate rows when using left join. add a row number within each group of dates, so that only the first June from df_2 will be joined to the first June entry from df_1. 
us.recent.region <- left_join(
          state %>% group_by(state, date) %>% mutate(id = row_number()),
          us.recent[,c("Region","state")] %>% group_by(state) %>% mutate(id = row_number()),
          by = c("state", "id"))


us.region <- us.recent.region %>%
                        na.omit() %>%
                        filter(date == (Sys.Date()-2)) %>%
                        subset(select = c("cases","deaths","Region")) %>%
                        group_by(Region) %>%
                        summarise(cases.two = sum(cases), deaths.two = sum(deaths))

us.region.three <- us.recent.region %>%
                        na.omit() %>%
                        filter(date == (Sys.Date()-3)) %>%
                        subset(select = c("cases","deaths","Region")) %>%
                        group_by(Region) %>%
                        summarise(cases.three = sum(cases), deaths.three = sum(deaths)) 

us.region$cases.three <- us.region.three$cases.three
us.region$deaths.three <- us.region.three$deaths.three

# find the region counts for the past day
us.region$total <- (us.region$cases.two - us.region$cases.three)
us.region$deathtotal <- (us.region$deaths.two - us.region$deaths.three)

# calculate percent of all new cases by region
us.region$pct <- percent( us.region$total / (sum(us.region$total)),2)
us.region$dpct <- percent( us.region$deathtotal / (sum(us.region$deathtotal)),2)

# Specify label location in the pie graph (side note: Dont use pie graphs!)
# us.region <- us.region %>% 
#   arrange(desc(pct)) %>%
#   mutate(prop = total / sum(us.region$total) *100) %>%
#   mutate(ypos = cumsum(prop)- 0.5*prop )
# 
# 
# pie <- ggplot(us.region, aes(x="", y=pct, fill=Region)) +
#               geom_bar(stat="identity", width=1) +
#               coord_polar("y", start=0) +
#               theme_void() +
#               theme(legend.position="none") +
#               scale_fill_brewer(palette="Blues")

# Now we've made a nice (chicken) plot pie
# plot(pie)

# Bummer, doesn't render correctly in ggplotly and I'd rather not use the standard plot function. Switching over to highchart, huge shout out to # https://www.kaggle.com/tavoosi/suicide-data-full-interactive-dashboard/code 


Region_color <- (brewer.pal(4, "Blues"))

highchart() %>% 
  hc_add_series(us.region, hcaes(x = Region, y = total, 
                               color = Region_color), type = "pie") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", pointFormat = paste("Region: <b>{point.Region} ({point.percentage:.1f}%)</b> <br> Total <b>{point.y}</b>")) %>%
  hc_title(text = "<b>Cases by Region</b>", style = (list(fontSize = '14px'))) %>% 
  hc_subtitle(text = "Yesterday", style = (list(fontSize = '10px'))) %>%
  hc_plotOptions(pie = list(dataLabels = list(distance = 5, 
                            style = list(fontSize = 10)), 
                            size = 130)) 


```

### {.no-padding}

```{r fig.height=0.8}

highchart() %>% 
  hc_add_series(us.region, hcaes(x = Region, y = deathtotal, 
                               color = Region_color), type = "pie") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", pointFormat = paste("Region: <b>{point.Region} ({point.percentage:.1f}%)</b> <br> Total <b>{point.y}</b>")) %>%
  hc_title(text = "<b>Deaths by Region</b>", style = (list(fontSize = '14px'))) %>% 
  hc_subtitle(text = "Yesterday", style = (list(fontSize = '10px'))) %>%
  hc_plotOptions(pie = list(dataLabels = list(distance = 5, 
                            style = list(fontSize = 10)), 
                            size = 130)) 


```






Column {data-width=800}
-------------------------------------


### Cases Per Capita by County <font size='1'> Per Capita 10,000 </font>

```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=10}

leaflet(width = 750, height = 500) %>%
  addProviderTiles("CartoDB.Positron") %>%
  setView(-98, 39, zoom = 4) %>% 
  addPolygons(data = us.sp , 
              fillColor = ~uspal(us.sp$Confirmed_Per_Capita), 
              fillOpacity = 0.7, 
              weight = 0.2, 
              smoothFactor = 0.2, 
              popup = ~uspopup_t) %>%
  addLegend(pal = uspal, 
            values = us.sp$Confirmed_Per_Capita, 
            position = "bottomright", 
            title = "Quantile")
            
            
```


### State by State Summary <font size='1'> Per Capita 100,000 </font>

```{r, echo=FALSE}

formattable(state.formattable)

```

State {data-orientation=columns data-icon="ion-android-map"}
=======================================================================


Column {data-width=400}
-------------------------------------

### Top 10 Growth State's Trend

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=4}

time <- as.POSIXct(strptime(c("2020-01-22",latest_date), format = "%y-%m-%d"))
top.states <- top_n(ungroup(state.tbl), 10, `Past Week Change CPC`)

states.trend <- data %>% filter(`state` %in% top.states$State) %>%
                  group_by(date, state) %>%
                  summarise(cases = sum(cases)) %>%
                  ggplot(aes(x=as.POSIXct(date),y=cases, color=state)) + 
                  geom_point(size=.5) + 
                  geom_line(alpha=.5) + 
                  scale_x_datetime(limits =time) + 
                  scale_color_manual(values=Xtra_Blue) +
                  labs(title="") +
                  xlab("") + 
                  ylab("") +
                  theme(legend.title=element_blank())
                  
ggplotly(p= states.trend,
         width = 750, 
         height = 500)             
#plot(states.trend)

```

### Top 10 Case Growth Current Count

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=4}

lol.plot <- ggplot(top.states, aes(x=reorder(State,`Current Cases`), 
                                   y=`Current Cases`)) +
                  geom_segment( aes(x=reorder(State,`Current Cases`), 
                                    xend=reorder(State,`Current Cases`),
                                    y=0, 
                                    yend=`Current Cases`)) +
                  geom_point(size=5, 
                             color=drkblue, 
                             fill=alpha(drkblue, 0.3), 
                             alpha=0.7, 
                             shape=21, 
                             stroke=2) +
                  scale_y_continuous(name="Count", labels = scales::comma) +                
                  coord_flip() +
                  xlab("") +
                  labs(title="")

 
ggplotly(p = lol.plot,
         width = 750, 
         height = 500)             


```



Column {data-width=400}
-------------------------------------

### Case Growth by State

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=4}


p <- ggplot(state, aes(date, state)) + 
     geom_tile(aes(fill = cases)) +
     scale_fill_gradient(name="Confirmed Cases", 
                        low="white",
                        high=drkblue,
                        limits = c(0, 100000),
                        oob = scales::squish) +
     theme(panel.background=element_rect(fill="white", color="white"),
           plot.background = element_blank(),
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.border = element_blank()) +
     labs(title = "", 
          subtitle = "") +
     ylab("") +
     xlab("") + 
     theme(legend.position="none")



#plot(p)

ggplotly(p = p,
         width = 750, 
         height = 500)

```


Counties {data-orientation=rows data-icon="ion-pin"}
=======================================================================


## Row 1 {data-height=400 .no-padding}


### Shortest Number of Days to 1000 Cases <font size='1'> Of all Counties with atleast 1000 cases </font>

```{r, echo=FALSE}

# of the counties which have 1000 cases and aren't missing a fips code (WHICH REMOVES NYC DAMNIT)
min.k <- data %>% filter(cases >= 1000 & !is.na(fips)) %>% arrange(date)
# grab those counties when they had between 0-1000 cases

t.cases <- data %>% filter(fips %in% min.k$fips & cases <= 1000)
# determine the number of days it took to get to 1000 cases
t.cases <-t.cases %>% group_by(fips) %>% mutate(id = row_number())
t.cases <-t.cases %>% group_by(fips) %>% mutate(id = 1:n())
t.cases <-t.cases %>% group_by(fips) %>% mutate(id = seq_len(n()))
t.cases <-t.cases %>% group_by(fips) %>% mutate(id = seq_along(date))

# the number of days it took a zip code, with at least 1000 cases to get to 1000 by fips
t.cases.max <- t.cases %>% 
                group_by(fips) %>% 
                summarise(id = max(id)) %>% 
                rename(NumDays = id)

# Find bottom 10 values and fips codes
max.tbl <- top_n(ungroup(t.cases.max), -10, NumDays)

max.tbl <- min.k %>% 
              filter(date==latest_date) %>% 
              subset(select=c("fips",
                              "cases",
                              "county",
                              "state")) %>%  
              left_join(max.tbl[,c("fips","NumDays")], by=c("fips"))  

# Reorder the columns for table
max.tbl <- max.tbl[c("fips",
                     "state", 
                     "county", 
                     "cases",
                     "NumDays")]

#save for plot
max.plt <- max.tbl %>%
            filter(!is.na(NumDays)) %>%
            subset(select = c("state",
                              "county",
                              "cases",
                              "NumDays")) %>%
            rename(State=state, 
                   County=county, 
                   Cases=cases, 
                   `Days to 1k`=NumDays) %>% 
            arrange(`Days to 1k`)
                    
                    

max.tbl <-  max.tbl %>%
            filter(!is.na(NumDays)) %>%
            subset(select = c("state",
                              "county",
                              "cases",
                              "NumDays")) %>%
            rename(State=state, 
                   County=county, 
                   Cases=cases, 
                   `Days to 1k`=NumDays) %>% 
            arrange(`Days to 1k`) %>%
            formattable(align =c("l","l","r","r"),
                list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
                `Days to 1k` = color_bar(ltblue)))


#formattable(max.tbl)

#createing a barplot because

max.plt$`State & County` = paste(max.plt$State,",",max.plt$County)

max.plt <- max.plt %>%
              mutate(name = fct_reorder(`State & County`, desc(`Days to 1k`))) %>%
              ggplot(aes(x=name))+
              geom_bar(aes(y=`Days to 1k`, fill=name),
                       stat="identity",
                       position ="identity",
                       alpha=.8) +
                    theme_classic() +
              scale_fill_manual(values=Xtra_Blue) +
                    theme(legend.position = "none") +
              coord_flip() +
                    labs(title="") +
                       xlab("") + 
                       ylab("Days")

ggplotly(p=max.plt,
         width = 750, 
         height = 500)


```


```{r, echo=FALSE, warning=FALSE, include=FALSE}

# Top case growth in past 7 and 30 days

growth <- data %>% filter(!is.na(fips)) %>% group_by(fips) %>% arrange(date)

# Reformatting the latest date as a data frame, renaming the column to last week to subtract 7 days, also create month df here as well
latest_date.df <- as.data.frame(latest_date) 
names(latest_date.df)[1]<-paste("Date")
LastWeek.df <- latest_date.df$Date - 7
LastMonth.df <- latest_date.df$Date - 30
LatestDate.df <- latest_date.df$Date

# Subset last 7, 30 days, and currnt value                                                         
tseven <- growth %>% filter(date == (LastWeek.df)) %>% rename(lastweek = cases)
tthirty <- growth %>% filter(date == (LastMonth.df)) %>% rename(lastmonth = cases)
tcurrent <- growth %>% filter(date == (LatestDate.df)) %>% rename(currentcases = cases)


# Join the last wee and last month totals to our current df
tcurrent <- tcurrent %>% left_join(tseven[,c("fips","lastweek")], by=c("fips"))
tcurrent <- tcurrent %>% left_join(tthirty[,c("fips","lastmonth")], by=c("fips"))

# Join current population and cases per capita from previous df above which of course uses GEOID
tcurrent <- tcurrent %>% left_join(us.recent[,c("fips","pop_2015","Confirmed_Per_Capita")], by=c("fips"))

# calculate rates per capita growth over past week and month
tcurrent$lastweek_percapita <- round(tcurrent$lastweek/tcurrent$pop_2015*10000,2)
tcurrent$lastmonth_percapita <- round(tcurrent$lastmonth/tcurrent$pop_2015*10000,2)

# % difference between current and previous values
tcurrent$lastweek_pc_delta <- round((tcurrent$Confirmed_Per_Capita - tcurrent$lastweek_percapita) / 
                                 ((tcurrent$Confirmed_Per_Capita + tcurrent$lastweek_percapita)/
                                    2)*100,2)
                               
                               
tcurrent$lastmonth_pc_delta <- round((tcurrent$Confirmed_Per_Capita - tcurrent$lastmonth_percapita) /
                                       ((tcurrent$Confirmed_Per_Capita + tcurrent$lastmonth_percapita)/
                                          2)*100,2)


# ID top quartile (> 75%) of postivie % change per capita over the past week and month
topweekgrowth <- subset(tcurrent, lastweek_pc_delta > quantile(lastweek_pc_delta, prob = 0.75, na.rm = TRUE))
# topweekgrowth$topweekgrowth <- 1
topmonthgrowth <- subset(tcurrent, lastmonth_pc_delta > quantile(lastmonth_pc_delta, prob = 0.75, na.rm = TRUE))
# topmonthgrowth$topmonthgrowth <- 1

topcurrentcasecount <- subset(tcurrent, Confirmed_Per_Capita > quantile(Confirmed_Per_Capita, prob = 0.75, na.rm = TRUE))
# topcurrentcasecount$topcurrentcasecount <- 1


# Find the bottom 25% growth per capita week/month
lowestweekgrowth <- tcurrent %>% filter(fips %in% min.k$fips) %>% subset(lastweek_pc_delta < quantile(lastweek_pc_delta, prob = 0.25, na.rm = TRUE))
# lowestweekgrowth$lowestweekgrowth <- 1

lowestmonthgrowth <- tcurrent %>% filter(fips %in% min.k$fips) %>% subset(lastmonth_pc_delta < quantile(lastmonth_pc_delta, prob = 0.25, na.rm = TRUE))


# Lowest growth after 1000 cases (best containment)
# lpw.tbl <-  top_n(ungroup(lowestweekgrowth), -10, lastweek_pc_delta) %>%
#             subset(select = c("state","county","pop_2015","currentcases","Confirmed_Per_Capita", "lastweek_pc_delta")) %>%
#             rename(State=state, County=county, Population=pop_2015, `Current Cases`=currentcases, `Cases Per Capita (CPC/10k)`=Confirmed_Per_Capita, `Percent Increase CPC Past Week` = lastweek_pc_delta) %>% arrange(desc(`Percent Increase CPC Past Week`)) %>% 
#   arrange(`Percent Increase CPC Past Week`) %>%
#             formattable(align =c("l","l","r","r","r","r"),
#                 list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
#                 `Percent Increase CPC Past Week` = color_bar(ltblue)))
# 
# 
# formattable(lpw.tbl)





```


### Top 10 counties by cases per capita

```{r}

# Top cases per capita
cpc.tbl <-  top_n(ungroup(topcurrentcasecount), 10, Confirmed_Per_Capita) %>%
            subset(select = c("state","county","pop_2015","currentcases","Confirmed_Per_Capita")) %>%
            rename(State=state, County=county, Population=pop_2015, `Current Cases`=currentcases, `Cases Per Capita (CPC/10k)`=Confirmed_Per_Capita) %>% 
            arrange(desc(`Cases Per Capita (CPC/10k)`)) %>%
            formattable(align =c("l","l","r","r","r"),
                list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
                `Cases Per Capita (CPC/10k)` = color_bar(ltblue)))

#formattable(cpc.tbl)



# Swtich from table to bar graph
cpc.plt <-  top_n(ungroup(topcurrentcasecount), 10, Confirmed_Per_Capita) %>%
            subset(select = c("state","county","pop_2015","currentcases","Confirmed_Per_Capita")) %>%
            rename(State=state, County=county, Population=pop_2015, `Current Cases`=currentcases, `Cases Per Capita (CPC/10k)`=Confirmed_Per_Capita) %>% 
            arrange(desc(`Cases Per Capita (CPC/10k)`))

cpc.plt$`State & County` = paste(cpc.plt$State,",",cpc.plt$County)

cpc.plt.fnl <- cpc.plt %>%
              mutate(name = fct_reorder(`State & County`, desc(`Cases Per Capita (CPC/10k)`))) %>%
              ggplot(aes(x=name))+
              geom_bar(aes(y=`Cases Per Capita (CPC/10k)`, fill=name),
                       stat="identity",
                       position ="identity",
                       alpha=.8) +
                    theme_classic() +
              scale_fill_manual(values=rev(Xtra_Blue)) +
                    theme(legend.position = "none") +
                    labs(title="") +
              theme(axis.text.x = element_text(angle = 45)) +
                       xlab("") + 
                       ylab("Cases Per Capita")

ggplotly(p=cpc.plt.fnl,
         width = 750, 
         height = 500)

```

## Row 2 {data-height=400 .no-padding}

### Top Growth: Past Week

```{r, echo=FALSE, warning=FALSE}

tpw.tbl <-  top_n(ungroup(topweekgrowth), 10, lastweek_pc_delta) %>%
            subset(select = c("state","county","pop_2015","currentcases","Confirmed_Per_Capita", "lastweek_pc_delta")) %>%
            rename(State=state, County=county, Population=pop_2015, `Current Cases`=currentcases, `Cases Per Capita (CPC/10k)`=Confirmed_Per_Capita, `Percent Increase CPC Past Week` = lastweek_pc_delta) %>% arrange(desc(`Percent Increase CPC Past Week`)) %>%
            formattable(align =c("l","l","r","r","r","r"),
                list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
                `Percent Increase CPC Past Week` = color_bar(ltblue)))


formattable(tpw.tbl)


```


### Top Growth: Past Month

```{r, echo=FALSE, warning=FALSE}

tpm.tbl <-  top_n(ungroup(topmonthgrowth), 10, lastmonth_pc_delta) %>%
            subset(select = c("state","county","pop_2015","currentcases","Confirmed_Per_Capita", "lastmonth_pc_delta")) %>%
            rename(State=state, County=county, Population=pop_2015, `Current Cases`=currentcases, `Cases Per Capita (CPC/10k)`=Confirmed_Per_Capita, `Percent Increase CPC Past Month` = lastmonth_pc_delta) %>% arrange(desc(`Percent Increase CPC Past Month`)) %>%
            formattable(align =c("l","l","r","r","r","r"),
                list(State = formatter("span", style = ~ formattable::style(color = "grey",font.weight = "bold")),
                `Percent Increase CPC Past Month` = color_bar(ltblue)))

formattable(tpm.tbl)

```


info {data-orientation=rows data-icon="ion-ios-information-outline"}
=======================================================================

```{r fig.height=0.8}

cat("Updated daily at 9:31am, Data current as of:\t",format(as.POSIXct(format((Sys.Date()-2)))))

```

### Acknowledgement 

This dashboard is an interpretation of my other COVID projects [HERE](https://www.kaggle.com/mcnamamj/us-county-spread-sir-mice-svm) and [HERE](https://www.kaggle.com/mcnamamj/covid-19-graphing-and-mapping).

Other information available at [FlexDashboard](https://rmarkdown.rstudio.com/flexdashboard/) and the [R Graph Gallery](https://www.r-graph-gallery.com/). Icons from [ionicons](https://ionicons.com/v2/cheatsheet.html)


###

###



